\LARGE Performance Evaluation of Xenomai 3

### 2015-10-20 paper.tex
Combine 2 kernel config section into one
config/patch table not yet added

\begin{abstract}
Xenomai 3 is the new architecture of the real-time framework running seamlessly side-by-side Linux as a dual-kernel system like Xenomai 2, or natively over mainline Linux kernels supplemented by the PREEMPT\_RT efforts to meet stricter response time requirements than standard kernel preemption would bring. In this presentation, we will evaluate the performances of Xenomai 3 running with both configurations and analyze the various benchmarks for ARM Cortex-A series. Xenomai 3 introduces some optimizations over RTOS API emulation, thread-to-thread communications, and significantly lower overhead with dual-kernel configurations. The comprehensive performance comparisons illustrate the major evolution of Xenomai 3 along with the revised Real-Time Driver Model (RTDM) which provides a unified interface over both PREEMPT\_RT and dual-kernel.

@@

\subsubsection{Hardware}
BeagleBone Black, an effective embedded platform with ARM Cortex-A8 processor, capable of running Linux and Xenomai (both 2 and 3), consisting of a single processor, a 512 MB memory, 32kB L1 caches and a 256kB L2 cache.

\subsubsection{Kernel}
A Linux kernel that can be patched with PREEMPT\_RT, Xenomai 2 and Xenomai 3 is needed for the experiment (Xenomai 3 has to run on Linux kernel 3.10 or later versions). Linux 3.14 is selected for our experiment. In some cases when the patches couldn't be successfully applied on the kernel, we tried to resolve the conflicts manually.

\subsubsection{Kernel configuration }
Some of the kernel conﬁguration options may have an impact on real-time latencies. These options include all options under CPU Power Management, APM support, and Opportunistic sleep. Additionally, most debug options in Kernel hacking section lead to increased latencies. Those options are disabled before compilation.

@@

\bibliographystyle{plain}
\begin{thebibliography}{9}%use this if you have <=9 bib refs
	\bibitem {rtai}{\it https://www.rtai.org/}
	\bibitem {sel4}{\it http://ssrg.nicta.com.au/projects/seL4/}
\end{thebibliography}

>>>>

\begin{abstract}
Xenomai 3 is the new architecture of the real-time framework running seamlessly side-by-side Linux as a dual-kernel system like Xenomai 2, or natively over mainline Linux kernels supplemented by the PREEMPT\_RT efforts to meet stricter response time requirements than standard kernel preemption would bring. In this presentation, we will evaluate the performances of Xenomai 3 running with dual-kernel configuration and analyze the various benchmarks for ARM Cortex-A series. Xenomai 3 introduces some optimizations over RTOS API emulation, thread-to-thread communications, and significantly lower overhead with dual-kernel configurations. The comprehensive performance comparisons illustrate the major evolution of Xenomai 3 along with the revised Real-Time Driver Model (RTDM) which provides a unified interface over both PREEMPT\_RT and dual-kernel.

@@

\subsubsection{Hardware}
For the testing platform, we used the BeagleBone Black. BeagleBone Black is an effective embedded platform with ARM Cortex-A8 processor, capable of running Linux and Xenomai (both 2 and 3), consisting of a single processor, a 512 MB memory, 32kB L1 caches and a 256kB L2 cache.

\subsubsection{Linux Kernel}
We installed a Debian Linux image\cite{debian} on the beaglebone, with hardware-specific linux kernel from\cite{kernel}. Kernel version 3.14.39 were chosen due to it's compatibility with all kernel configurations.
Four distinct kernel configurations are used for the experiment, as summarized in table\ref{table:config}. Kernel are patched using git merge first, and remaining conflicts are resolved manually.

Kernel conﬁguration options are mostly left as default. However, some of the options may have an impact on real-time latencies. These options include all options under CPU Power Management, APM support, and Opportunistic sleep. Additionally, most debug options in Kernel hacking section lead to increased latencies. Those options are turned off before compilation.

% TODO : add config table

@@

\bibliographystyle{plain}
\begin{thebibliography}{9}%use this if you have <=9 bib refs
	\bibitem {rtai}{\it https://www.rtai.org/}
	\bibitem {sel4}{\it http://ssrg.nicta.com.au/projects/seL4/}
	\bibitem {debian}{\it http://debian.beagleboard.org/images/bone-debian-7.5-2014-05-14-2gb.img.xz}
	\bibitem {kernel}{\it https://github.com/beagleboard/linux}
\end{thebibliography}
